% Put your abstract here

\begin{abstractwithpageno}	
International School Manila (ISM) has extensive collection of Academic and Administrative Reports that are crucial for accreditation, audits and external verification, and the authenticity and integrity of these reports is critical. Currently, no cryptographic bindings exist between the reports and their metadata in centralized storage systems, which can be modified without being detected, and which have no IT-independent audit trails or slow verification. 

This project suggests a \textit{hybrid platform} called \textbf{VERACISM} (\textit{Verifiable Academic Records for ISM}) that will allow to attach finalized reports to decentralized content-addressed storage while maintaining identity, access control, and operational monitoring within the governance of ISM. Reports are created with the existing ISM applications are uploaded via api integreation. In VERACISM,scanned files were validated using ClamAV and YARA, and by MIME type and file size, then hashed with SHA-256, and written to IPFS with Filecoin-backed deals, using Lighthouse. The file is given a unique Content Identifier (CID) and is stored with report metadata and immutable audit events in MSSQL under strict RBAC/ABAC rules. 

Both a web-based console and a public verification portal enable tenant and integrator administration and provide both internal and external parties with the ability to verify report integrity via CIDs or QR codes, with an optional option of cross-checking storage evidence in public explorers. 

The project is implemented using a DevSecOps lifecycle approach which includes secure design, automated checks of security and scheduled VAPT, following the OWASP Top 10 risks. Planned evaluation integrates task-based user testing for administrator, tenant offices, integrators and verifiers, structured security testing and defined acceptance criteria. 

VERACISM will help enhance the record governance of ISM, lower verification overhead, and offer a pattern for storing academic records in a tamper-proof fashion.
\end{abstractwithpageno}
