% Put your acknowledgement here

\begin{acknowledgement}
The researcher wishes to convey profound gratitude to all individuals and
offices who played a role in bringing this capstone project to fruition,
entitled “\textbf{VERACISM}: \textit{Verifiable Academic Records for International School
Manila.}”

Heartfelt thanks go first to my project adviser, \textbf{KATRINA JOY M.\ ABRIOL-SANTOS}, for her constant guidance, timely feedback and patience in the process of writing this proposal and designing this study. Her feedback and suggestions to the project on scope, structure and technical aspects were pivotal in developing the system concept, and the manuscript.

The researcher also extends his appreciation to each member of the panel for the questions that they raised and the tips that are provided to strengthen the problem statement and to make the methodology more valid and in line with the needs of the institution while maintaining the technical validity of VERACISM. 

The school's appreciation also goes to \textbf{International School Manila} for sharing their current practices and issues with report authenticity, verification and long-term maintenance of reports. They helped to develop the needs of the project, use cases and the whole VERACISM workflow. 

The researcher also acknowledges the technical advice, detailed review and constant support provided by the \textbf{IT Development Team} during the project development. 

Last but not least the researcher would like to thank his family members and friends for their encouragement, patience and understanding during the countless hours he spent researching, writing and developing a system. These constant sources of encouragement helped us to persevere and complete this work. 

More than anything else, the researcher expresses gratitude to \textbf{God} for his grace, power and perseverance in the completion of this work. \textbf{SALAMAT SA DIOS !} 

\end{acknowledgement}
