\section{INTRODUCTION}
    \subsection{Background of the Project}

International School Manila (ISM) handled a wide range of academic and administrative reports that had to remain authentic, traceable, and tamper-proof. These records provided accountability, accreditation and academic credibility. Under ISM's standard process, reports were generated using various applications and uploaded directly to on-premise servers or cloud storage via various APIs that each created one student record. This process had no immutability version tracking nor an audit trail. Files or metadata could be modified or replaced without a durable record of who changed what and when. Since there was no cryptographic binding between a stored file and its database record, undetected alterations were possible and unverifiable. When reports were shared or reviewed, external parties such as colleges and universities had no independent way to prove that the files matched the originals released by ISM. This required multiple email exchanges between ISM and the external organization. The absence of tamper-evidence and end-to-end traceability weakened ISM's data governance and institutional trust.

The volume of existing records gave this risk concrete institutional consequences. Between 2014 and 2025, ISM's student report repositories, which covered report cards, CAS reports, Measures of Academic Progress results, and related documents, already contained \textbf{112,612 files}, with a further \textbf{16,108 files} generated by Finance. As of 2025, ISM had \textbf{2,445} active students, each of whom accumulated dozens of academic and financial records even before alumni and long-term archives were counted. In such an environment, just a minor inauthenticity, provenance or version control issue could impact tens of thousands of files simultaneously.

Given these circumstances, those using the reports inside ISM had no easy way to trace the history of a file over time, and no way to witness the tampering of a report. They would have had to rely on the assumption that what in front of them was the “correct” version that the institution had intended because they didn't check a cryptographic record that proved the report was unchanged. This dependence on institutional assurances, as opposed to mathematically proven proof, over time had proven to be an operational and compliance risk \citep{Cflow2025,Encrypthos2025,NRC2005,SimpleButNeeded2025}. Therefore, there was uncertainty when the audit was performed and when the accreditation review was performed and when the interdepartmental review was performed. The process was slow, manual and IT-dependent, particularly as there was a possibility of multiple copies of the same file existing in different systems.

In various industries, such as universities, hospitals, financial institutions, and others, teams implemented various partial solutions, such as cloud storage versioning, checksums, or IPFS pinning services, to enhance the recovery and tracking of files. IPFS (InterPlanetary File System) was a decentralized, peer-to-peer protocol used for data storage and sharing via content-addressed identifiers, where every file was identified by a cryptographic hash instead of a server address.\citep{IPFSDocs2025,CryptoSTIPFS2025}. These tools improved the resilience, but typically were just standalone utilities, running away from the day to day activities of academic offices. Their guarantees were still reliant on the logs within their local systems and ecosystem trust, rather than on an end-to-end, independently verifiable trail.\citep{AWSS3Versioning2025,NIST80092r1,FilebasePinning2025,PinataPinning2025,SchneiderIPFSPinning2025,BlockchainReporterIPFS2025}.

To fill this gap, \textbf{VERACISM} (Verifiable Academic Records for ISM) introduced content-addressed, decentralized persistence for reports storage and verification. ClamAV and YARA were used to scan each uploaded report, which was validated by MIME type and size, then hashed using SHA-256, and stored on the Lighthouse system on IPFS with deals backed by Filecoin. A different Content Identifier (CID) is generated for each file the moment there is a change in content, thus ensuring tamper resistance and publicly verifiable. A secure upload for both .NET 8 Web API (MSSQL) and tenant-aware metadata and immutable audit events were watched, and they had strict RBAC/ABAC. Verification took place at the portal level by QR or CID lookups which re-hashed content and compared it with evidence of deals on Filfox without the need of ISM credentials. The baseline integrity, permanence and independent verification was achieved by fully content-addressed, decentralized storage. If additional needs came along, such as rules for access, payment or cross-application automation on the blockchain, it was reserved for future versions.

VERACISM adopted an architecture that was a mix of on-premise control and decentralized permanence. ISM assumed control of identity, access restrictions, metadata and operational audit trails in its trusted space, while content integrity and long-term durability were backed up by public decentralized infrastructure, such as IPFS/Filecoin, which can be independently verified. This model enabled full flexibility of existing workflows and compliance controls and made the proof of integrity easily verifiable, without depending on the trustworthiness of ISM systems.

The goal of VERACISM was to break the cycle of implicit trust for explicit proof, long term and visible record keeping, and easier audits. The proposed system sought to enhance the credibility of institutions, minimize the cost of verification checks, and to overcome report modification by silence or by unauthorized third parties by applying cryptographic integrity, decentralized data storage, and an outer layer of verification.

    \subsection{Objectives}

The proposed system was designed to modernize and secure creation, storage and independent verification of ISM academic reports with the help of content-addressed decentralized infrastructure, namely IPFS/Filecoin with the help of Lighthouse. The main goal was to eliminate hacks, and simplify verification with CID , QR-based and File upload checks, which would give cryptographic, tamper-evident proof of integrity, without the need of smart contracts.

    \subsection{Specific Objectives}
\begin{enumerate}
  \item Implement file security check and validation of file type.
  \item Designed and developed web application which used role-based access control.
  \item Defined a threat model and mitigations such as input sanitisation, rate limits, CSRF, key rotation and least privilege.
  \item Clearly and effectively designed, developed and applied integration, security and performance testing with clear success criteria – including correct end-to-end handling of reports across integrated systems, no critical/High severity security findings, response times and throughput were maintained within agreed service levels under agreed load etc.
  \item Deployed, maintained and provided runbooks for backup and restore, monitoring, incidents, and compliance.
\end{enumerate}

    \subsection{Scope and Limitations}

The system maintained immutable storage, verification and controlled retrieval of finalized reports, complete audit trail and cryptographic proof of integrity. It did not create any report content, or supplant academic systems. These were some of the project boundaries, goals and benefits summarized:

        \subsubsection{Scope}
        \begin{itemize}

            \item Verification Portal
                \begin{itemize}
                    \item Made CID lookup and file upload capabilities in the portal available for independent validation, without the need for ISM credentials.
                \end{itemize}
                
            \item Document Security Feature
                \begin{itemize}
                    \item Included pre-upload security controls, such as ClamAV, YARA rules, MIME validation, size validation and quarantine workflow.
                    \item Content-addressed storage through Lighthouse with IPFS/Filecoin.
                    \item Computed SHA-256 hashing and CID revalidation during verification.
                \end{itemize}
                
            \item Events/Access Management
                \begin{itemize}
                    \item Provided REST APIs for upload, metadata retrieval, verification, and controlled download.
                    \item Stored tenant-aware metadata and immutable audit events in MSSQL.
                    \item Implemented role-based and attribute-based access control with scoped API keys.
                    \item Performed scheduled health checks for CID availability, replica status, and retrieval latency.
                    \item Provided structured logging, alerting, and runbooks for operations across Dev, UAT, and Production.
                \end{itemize}
                
            \item Integration
                \begin{itemize}
                    \item Integrated API endpoints with existing ISM applications through approved service accounts.
                \end{itemize}

        \end{itemize}


VERACISM was integrated with completed institutional reports, guaranteeing long term claims that are integrity and traceable, while also being auditable, and without the need of the original party to ensure the integrity of the report. VERACISM is equivalent to secure intake/scanning/hashing, and decentralized storage and metadata registration/digestion/verification of documents per registered hashes (with whitelisted ISM workflows). Instead it was designed to be integrated with existing academic administration systems that could be used to create and/or manage student information, but were not designed to be a replacement to the systems used by students to create and/or manage student information. VERACISM did the research on the aforementioned threats and reported on the following: Tamper evidence, auditability, controlled access and continued compatibility with ISM existing systems.

        \subsubsection{Limitations}
            \begin{itemize}
              \item Report authoring or workflow approvals.
              \item Replacement of SIS or LMS and non-records business functions.
              \item Smart contracts implementation and on-chain access rules, or payment logic.
              \item Student self-service uploads.
              \item Semantic content moderation beyond malware and known bad pattern checks.
              \item User crypto wallet management or token handling.
              \item Automated retry mechanism for transient Lighthouse storage failures; a document that passed scanning might not have been anchored to IPFS if the Lighthouse service was temporarily unavailable.
              \item The audit log UI did not enforce tenant-level scoping; audit metadata visibility was limited to the Admin role.
              \item The public verification endpoint was tested with 100 virtual users and a more comprehensive load test of the entirety of the scan-upload pipeline was beyond the scope of the project.
              \item During UAT testing, redirect links were not found on Administrator dashboard / Tenant Dashboard cards, which was in scope for the next development phase.
            \end{itemize}

VERACISM is not designed for report generation/workflows, report grading workflows, Self Service Portal uploads or Enterprise document management solutions. Other improvements include more advanced load testing, automatic retries and more detailed drilling within the dashboard. These options were removed, so that the initial release could concentrate on the main challenge: to provide signed off records to be verified, immutable and auditable.