% Summary and Conclusion

\section{SUMMARY AND CONCLUSION}

\subsection{Summary}

This study is composed from ones that designed, developed, and evaluated a decentralized academic document verification platform called \textbf{VERACISM}, \textit{Verifiable Academic Records for International School Manila (ISM)} for UPOU (University of the Philippines Open University). Incorporating cryptographic integrity verification, decentralized Web3 storage, and multi layered threat scanning into one platform, the system tackles the chronic issue of academic credential fraud.

VERACISM follows a multitenant model where the documents are individually-managed by the different educational institutions (tenants) sharing infrastructure of the platform itself. The main workflow is divided into three steps: (1) upload of documents to the system, (2) uploaded documents are checked in real time for malware and phishing using the ClamAV, YARA rules, and (3) PDF analyzer; the uploaded documents are encrypted and stored on the decentralized storage system Filecoin/IPFS, generating a tamper evident Content Identifier, CID; any participant in the system can check the authenticity of a document by resolving the CID and comparing the resulting file SHA-256 hash with the original document.

The system was subjected to five test processes namely, functional and integration test, performance test, security test and user acceptance test.

All the evaluations activities carried out were based on the baseline established in the Project Assessment chapter, among which a hybrid test strategy was implemented, an automated API execution along with manual role verification tests.

\subsubsection{Functional and Integration Testing}

Automated testing ran a set of \textbf{182 assertions} in 41 test cases,including 22 integration test cases, 93 assertions, for the scan, upload, report retrieval, CID verification, download, and storage workflows, and 19 functional test cases, 89 assertions exercising role based access control for the Admin and Tenant roles. \textbf{Automated test passed on 182 assertions all with 100\% rating.}
 (see Appendix~\ref{appendix:integration-tests}
and Appendix~\ref{appendix:functional-tests}).

There were 30 test cases covering Admin and Tenant workflows that were tested for using Role based manual and code review method. Of these, \textbf{27 passed fully} (90.0\%), \textbf{2 passed partially} (6.7\%), and \textbf{1 failed} (3.3\%). The single unsuccessful TC, "TC-ITO-005" exposed the lack of a re-retry mechanism should the Lighthouse storage service go unavailable, thereby putting the system at risk for transitory upload failures. Two “partial” results stood out as lacking some level of scoped audit log visibility in the UI, TC-ITO-006, and missing a \texttt{VerificationLog} write when a document is verified in the public, TC-E2E-003. These are three defects that have been documented and in the Future Work section these are focused upon. In spite of these items, the fundamental document lifecycle operations of ‘upload', ‘scan', ‘store', ‘retrieve' and ‘verify', functioned as expected for the evaluated scenarios.

\subsubsection{Performance Testing}

This performance evaluation was done with k6, with 100 VUs and 100 sustained VUs, during two sessions at the public CID verification endpoint.

The first version, \textbf{Version 1.0}, had a higher failure rate, but it was not due to issues at the application layer, but due to an Nginx rate limiting policy which was limiting concurrent requests to only a certain number before sending them to the application. Following the rate limitations adjustment, the second iteration (\textbf{Version 1.1}) showed a \textbf{had a much lower error rate}, thus confirming the performance of the application layer under the tested load. Both runs showed that latencies were within acceptable limits, and P95 time values were similar to the overhead for decrypting and streaming content from the Lighthouse proxy.
A summary of both rounds is provided in
Appendix~\ref{appendix:performance}.

The results met the desired performance criteria from the Project Assessment baseline which included stable availability with concurrent traffic, desirable response characteristics, and observation of root cause explanation in order to see why there were errors.

\subsubsection{User Acceptance Testing}

Role based task scripts were completed and user acceptance testing was done using the same. The executed UAT cycle included 30 role based cases in all parts of the cycle (admin, tenant office, registrar, student, external verifier and cross role flow).

All responses made by participants provided in the form
\textit{VERACISM\_UAT - Form Responses 1.csv} were used for UAT scoring.

UAT was rated as role scoped responses, such that the choice of non applicable UAT was left blank, by design, for those that did not work in that role. In total across 16 recorded role scoped evaluations there were \textbf{15 Passed} (93.8\%), \textbf{1 partially completed} (6.2\%) and \textbf{0 failed} evaluations. All 8 UAT IDs had responses at the unique level of the case; 7 of the 8 were approved and 1 partially.

These are the results that end users are ready to receive in a controlled way and maintain visibility of the improvements they have registered in the roadmap.

\subsubsection{Security Testing}

Security assessment was performed in two phases. The first phase employed Burp Suite
Community Edition as a Dynamic Application Security Testing (DAST) tool and produced several
tentative findings including SQL injection and reflected XSS candidates. Upon investigation, all
SQL injection findings were determined to be false positives: the backend exclusively uses Entity
Framework Core with parameterized queries, eliminating the SQL injection attack surface.
Like reflected XSS candidates, these were also scanned through the Angular frontend, which prevents any type of output encoding in the context above.

The second phase involved manual security testing and review of remediation level on the code to validate the results of the first phase. During this phase, it was determined that many results obtained on the first pass with DAST were false positives, and therefore not vulnerabilities. After the validation, the team pinpointed
and validated
\textbf{five genuine vulnerabilities} (VUL-01 through VUL-05) with severity ranging from Low to Medium-High. All five were made good before check-up:

\begin{itemize}
    \item \textbf{VUL-01} (Low): Verbose error messages were produced that gave insights into stack traces;
          this may be addressed via generation of generic responses to include error messages.
    \item \textbf{VUL-02} (Medium-High): Missing \texttt{INTERNAL\_API\_KEY} enforcement on the
          Lighthouse encryption service; remediated by implementing API key middleware.
    \item \textbf{VUL-03} (Low-Medium): Temporary files uploaded by this service are not deleted after
          processing; Remediated by adding deterministic cleanup logic.
    \item \textbf{VUL-04} (Medium-High): Missing \texttt{GET /health} endpoint may lead to
          healthcheck failures for a Docker image; Remediated by adding the health endpoint.

    \item \textbf{VUL-05} (Medium-High): Instantiating an \texttt{HttpClient} without using
          the abstraction from the classes \texttt{LighthouseStorageService} abstraction; remediated by all Lighthouse calls being routed through the service layer.

\end{itemize}

Details about vulnerabilities and remediation can be found in the security 
Appendix~\ref{appendix:security}.

The security responses were also in line with the Project Assessment
baseline, which listed boundary access verification, safe error handling, and evidence based review of the content of the scanners.


% -----------------------------------------------------------------------
\subsection{Conclusion}

Overall, these findings show that VERACISM is a \textbf{operationally validated, security hardened,
and reasonably performant} platform for decentralized academic credential verification, which performs reasonably well across a diverse group of users. It meets the basic goal of the system: allow educational institutions to upload student documents, attach cryptographic integrity proofs to these files in a decentralized network and empower any stakeholder to independently verify the validity of the student documents without access to a central authority or trusted party.

The automated test suite had a \textbf{100\% successful pass rate}, while the manual test suite
had a \textbf{90.0\% full pass rate} with limited gaps remaining just for noncritical feature, retry logic, audit log scope and verification log persistence. The gaps are not a risk to the fundamental verifier guarantee and are defined as a progression on the roadmap.

The security of VERACISM was significantly strengthened throughout the development process. All five confirmed vulnerabilities were mitigated, and the DAST SQL injection results were removed through architectural decision - instead of performing queries with user-supplied input, they are all formulated and passed as parameters through the entire solution. The system is free from any known critical or high severity vulnerabilities post remediation.

Performance testing showed that application layer is able to support moderate concurrent load without service degradation (100 VUs) with the correct infrastructure level rate limiting, when the number of expected requests is matched. That Nginx rate limiting misconfiguration was discovered in Version 1.0, and that the issue was resolved in Version 1.1 is a good result in itself, showing the implications of performance testing: it brought a real infrastructure bug to the surface which would not have been caught by functional testing alone.

\subsubsection{Contributions}

This study brings contributions in the following areas: (1) a working open source reference implementation of a decentralized document verification system namely Web3 storage, (2) a DevSecOps integration pattern between ClamAV, YARA and PDF phishing analysis in the document ingestion pipeline, (3) empirical evidence for functional testing, integration testing, performance testing, and the platform's security testing, and (4) documented vulnerability remediation lifecycle that supports similar academic information systems built in confined institutional settings.

VERACISM sets the groundwork for subsequent research into blockchain anchored academic credential systems, privacy preserving verification protocols, and interoperability standards with other systems like the W3C Verifiable Credentials and Open Badges.
